Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-14 paper/abstraction/appendix.tex
update examples for consistency
stashing changes

\newcommand{\sysname}{{\small \sf Methane}\xspace}
\newcommand{\sysnamesec}{{\sf Methane}\xspace}
\newcommand{\propane}{{\small \sf Propane}\xspace}

@@

\subsection{Methane}

The full \sysname syntax as well as expansions from constraints into regular expressions are shown in Figure~\ref{fig:syntax}. The language includes constraints of the form $\CD{\Agg(pfx, \ensuremath{r_1 \rightarrow r_2})}$ that say that aggregation for summary prefix $\CD{pfx}$ will occur from any single location matching $\CD{\ensuremath{r_1}}$ to any location matching $\CD{\ensuremath{r_2}}$. For simplicity, we prove the substitution property for \sysname for the fragment without aggregation.

\begin{figure*}[h!]\small
  \begin{minipage}[t]{.45\linewidth}
  \hdr{Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
    \hline%

     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
     pfx     &::=& d.d.d.d/[d..d] & \textit{prefix} \\
     t       &::=& \$x & \textit{template variable} \\
         &\BNFALT& pfx & \textit{prefix test} \\
     r       &::=& l & \textit{location} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT r & \textit{path negation} \\
         &\BNFALT& r^* & \textit{iteration} \\
     cc     &::=& agg(pfx, r_1 \rightarrow r_2)  & \textit{control constraints} \\
  \end{array} \]%

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}\small
  \hdr{Expansions}{}
  \vspace*{-1\baselineskip}
  %
  \[\begin{array}{rcl}
    \hline
    \Any               & = & \Sigma^* \\
    \None              & = & \emptyset \\
    \Internal          & = & \In^+ \\
    \Always(X)         & = & X^* \\
    \Never(X)          & = & (!X)^* \\
    \Through(X)        & = & \Sigma^* \cdot X \cdot \Sigma^* \\
    \End(X)            & = & \Sigma^* \cdot X \\
    \Start(X)          & = & X \cdot \Sigma^* \\
    \Enter(X)          & = & \Sigma^* \cdot \Out \cdot (X \cap \In) \cdot \Sigma^* ~ \cup \\
                       &   & \Sigma^* \cdot (X \cap \Out) \cdot \In \cdot \Sigma^* \\
    \Exit(X)           & = & \Sigma^* \cdot \In \cdot (X \cap \Out) \cdot \Sigma^* ~ \cup \\
                       &   & \Sigma^* \cdot (X \cap \In) \cdot \Out \cdot \Sigma^* \\
    \LinkKW(X,Y)       & = & \Sigma^* \cdot X \cdot Y \cdot \Sigma^* \\
    \PathKW(\vec{X})   & = & \Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^* \\
    \Novalley(\vec{X}) & = & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
                       &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
  \end{array} \]%

@@

  \hrulefill%
  \vspace{1em}

  \caption{Methane syntax and expansions.}
  \label{fig:syntax}
  %\vspace{-1em}
\end{figure*}%

\subsection{BGP Configuration}

\para{Syntax}

\vspace{2em}
\begin{figure*}[t!]\small%

  \hrulefill%

  \vspace{1em}%
  \begin{minipage}[t]{.46\linewidth}
  \hdr{ABGP Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     d    &   & & \textit{integer} \\
     c    &   & & \textit{community} \\
     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\%
  \end{array} \]%%

  \end{minipage}
  %
  %
  \begin{minipage}[t]{.5\linewidth}
  \hdr{Compilation}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(G.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_i,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
     \\
     \text{compile}( p_1, \dots, p_k, G) = \\
     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G), G) \\
  \end{array} \]%
  \end{minipage}%

  \vspace{1em}
  \vspace{1em}%

  \vspace*{-2\baselineskip}
  \begin{minipage}[t]{1.01\linewidth}
  \hdr{Policy Concretization}{}
  \vspace*{-2\baselineskip}
  %
  \[ \begin{array}{lcl}
     \\
     \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
     \Con(l, \Gamma, f)              &=& \Sigma_i ~ f_i^{-1}(l) \\
     \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
     \Con(r_1 \cap r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cap \Con(r_2,\Gamma,f) \\
     \Con(!r, \Gamma, f)             &=& !\Con(r,\Gamma,f) \\
     \Con(r^*, \Gamma, f)            &=& \Con(r,\Gamma,f)^* \\%
     \Con(\Pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&
          \Pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\%
     \Con(\$x ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&%
         [~ \Pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~, \\%
         & & ~~~~~~~~~~~~~~~ \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (\Pfx,l) \in \Gamma(x) ~]  \\%
     \Con(p_1, \dots, p_n, \Gamma,f) &=& \Con(p_1, \Gamma,f), \dots, \Con(p_n, \Gamma,f) \\%

@@

  \vspace{1em}
  \vspace{1em}%

  \begin{minipage}[t]{\linewidth}
  \hdr{ABGP Concretization}{}
  \vspace*{-2\baselineskip}
  %
  \[ \begin{array}{lcl}
     \\
     \Con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G)
        & = &
        \mathit{append}_i~ [~ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) ~]
        \\
     \Con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
        & = &
        \Con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, \Con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
        \\
     \Con(\Pfx \rightarrow {pc},\ell,\Gamma,f,G)
        & = &
        \Pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
        \\
     \Con(\$x \rightarrow {pc},\ell,\Gamma,f,G)
        & = &
        [~ \Pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (\Pfx, l) \in \Gamma(x) ~]
        \\
     \Con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G)
        & = &
        \Con(ma_1,o,\ell,\Gamma,f,G), \dots, \Con(ma_k,o,\ell,\Gamma,f,G)
        \\%
     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G)
        & = & \textbf{if}~ ns_1 = \{\text{start}\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)%

@@

  \caption{ABGP syntax, compilation from product graphs, policy concretization, and ABGP concretization.}
  \label{fig:concretization}
\end{figure*}%

\para{ABGP language}

We introduct a simple language for BGP configurations called ABGP. Figure~\ref{fig:concretization} shows the syntax for an ABGP policy. An ABGP policy maps topology locations $l$ to router configurations $rc$. Each router configuration $rc$ is a sequence of predicates $t$ and their corresponding configuration $pc$. A prefix configuration $pc$ is a sequence of match actions. Each match action $ma$ consists of a preference value $d$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $c_1$ expected from those neighbors, as well as export neighbors $ns_2$ and the community value $c_2$ to attach before sending to those neighbors.%

\para{Compilation}

Figure~\ref{fig:concretization} defines compilation from a \sysname policy to an ABGP policy. It starts by compiling ($\text{compile}_\text{PG}$) separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$. The function $\text{compile}_\text{PG}$ returns the test $t_i$, product graph $PG_i$, and the preference ordering $ord_i$.
%
The function $\text{compile}_\text{ABGP}$ then takes a sequence of tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy. For each internal router, it looks at each set of neighbor with the same community state $q_n$ and matches any of those neighbors with the preference provided by the ordering $ord$. It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.%

We assume a particular router $l$ appears at most once in any abgp specification.
We build configs using list-comprehension notation. For instance,
$[~ l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc) ~]$ denotes the abgp policy
%
\[ \begin{array}{c}
  l_1 \rightarrow rc_{1},... \\
  ...           \\
  l_k \rightarrow rc_{k},... \\
\end{array} \]

@@

We also define concretization over the ABGP policy in a similar manner. We replace each abstract router configuration $l \rightarrow rc$ a new entry for each concrete location $\ell \in f^{-1}(l)$. The concrete location $\ell$ is passed as a parameter to $con$ to remember the current router.
%
To concretize a prefix policy with a template ($\$x \rightarrow pc$) we replace it with a sequence of policies, one for each prefix in context ($(pfx,l) \in \Gamma(x)$). Match action statements where the set of import neighbors is the singleton set containing the product graph start node $\{ start \}$ and we are not currently at looking at the router configuration for the location specified in the context $l$, then we drop the match action. This is denoted with the $\bullet$ symbol. Finally, to concretize a set of neighbors, we again use $f^{-1}$ to find the set of concrete neighbors under the inverse homomorphism, but then restrict it to those that are actually connected in the underlying concrete topology with $G.E$.

@@

The goal of this section is to prove that the concretization and compilation functions commute: 
$$con(compile(pol,G^A),\Gamma,f,G) = compile(con(pol,\Gamma,f), G)$$ 
That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values on after compilation is complete. Note that the theorem states that the resulting ABGP policies are actually syntactically equivalent and not semantically equivalent. First we need a few helper theorems about compilation.

@@

    \[ \begin{array}{ll}
        & compile(con(pol,\Gamma,f), G)  \\
                          & \\
                         =& compile_{ABGP}( \\
                          &  ~~~~ compile_{PG}(pfx_{11} ~\Path~ r'_{111} ~\Prefer~,\dots, ~\Prefer~ r'_{11k},G ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{1j} ~\Path~ r'_{1j1} ~\Prefer~,\dots, ~\Prefer~ r'_{1jk},G ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{i1} ~\Path~ r'_{i11} ~\Prefer~,\dots, ~\Prefer~ r'_{i1k},G ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{ij} ~\Path~ r'_{ij1} ~\Prefer~,\dots, ~\Prefer~ r'_{ijk},G ) \\
                          &  ) \\
    \end{array} \]

@@

    \[ \begin{array}{ll}
        & compile(pol,G^A)  \\
                      & \\
                     =& compile_{ABGP}( \\
                      & ~~~~ compile_{PG}(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k}, G^A ), \\
                      & ~~~~ \dots, \\
                      & ~~~~ compile_{PG}(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r'_{ik}, G^A ), \\
                      & ) \\
    \end{array} \]

@@

  \[ \begin{array}{l}
     con(\textbf{compile}_\textbf{ABGP}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) ), \Gamma,f,G) \\
  \end{array} \]%

Unfold definition of $\text{compile}_\text{ABGP}$

@@

  \[ \begin{array}{l}
     = \textbf{compile}_\textbf{ABGP}( (pfx_{11},PG_{11},ord_{11}), \dots, (pfx_{ij},PG_{ij},ord_{ij}) ) \\
  \end{array} \]%

>>>>

\newcommand{\sysname}{{\small \sf Propane/AT}\xspace}
\newcommand{\sysnamesec}{{\sf Propane/AT}\xspace}
\newcommand{\propane}{{\small \sf Propane}\xspace}

@@

\vspace{2em}
\section{Definitions Reference}

\begin{figure*}[h!]\small
  \begin{minipage}[t]{.45\linewidth}
  \hdr{Propane/AT Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT cc & \textit{constraints} \\
     pfx     &::=& d.d.d.d/[d..d] & \textit{prefix} \\
     t       &::=& \$x & \textit{template variable} \\
         &\BNFALT& pfx & \textit{prefix test} \\
     r       &::=& l & \textit{location} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT r & \textit{path negation} \\
         &\BNFALT& r^* & \textit{iteration} \\
     cc     &::=& agg(pfx, r_1 \rightarrow r_2)  & \textit{control constraints} \\
  \end{array} \]%

  \end{minipage}
  %
  \begin{minipage}[t]{.5\linewidth}\small
  \hdr{Propane/AT Expansions}{}
  \vspace*{-1\baselineskip}
  %
  \[\begin{array}{lcl}
    \Any               & = & \Sigma^* \\
    \None              & = & \emptyset \\
    \Internal          & = & \In^+ \\
    \Always(X)         & = & X^* \\
    \Never(X)          & = & (!X)^* \\
    \Through(X)        & = & \Sigma^* \cdot X \cdot \Sigma^* \\
    \End(X)            & = & \Sigma^* \cdot X \\
    \Start(X)          & = & X \cdot \Sigma^* \\
    \Enter(X)          & = & \Sigma^* \cdot \Out \cdot (X \cap \In) \cdot \Sigma^* ~ \cup \\
                       &   & \Sigma^* \cdot (X \cap \Out) \cdot \In \cdot \Sigma^* \\
    \Exit(X)           & = & \Sigma^* \cdot \In \cdot (X \cap \Out) \cdot \Sigma^* ~ \cup \\
                       &   & \Sigma^* \cdot (X \cap \In) \cdot \Out \cdot \Sigma^* \\
    \LinkKW(X,Y)       & = & \Sigma^* \cdot X \cdot Y \cdot \Sigma^* \\
    \PathKW(\vec{X})   & = & \Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^* \\
    \Novalley(\vec{X}) & = & \NOT\PathKW(X_2,X_1,X_2) ~ \cap \dots \cap \\
                       &   & \NOT\PathKW(X_n,X_{n-1},X_n) \\
  \end{array} \]%

@@

  \vspace{1em}
  \begin{minipage}[t]{.46\linewidth}
  \hdr{mBGP Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     d    &   & & \textit{integer} \\
     c    &   & & \textit{community} \\
     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     mbgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{mBGP policy} \\%
  \end{array} \]%%

  \end{minipage}
  %
  %
  \begin{minipage}[t]{.5\linewidth}
  \hdr{Compilation}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \text{compile}_\text{mBGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(G.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_i,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
     \\
     \text{compile}( p_1, \dots, p_k, G) = \\
     ~~~~~~ \text{compile}_\text{mBGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G), G) \\
  \end{array} \]%
  \end{minipage}%

  \vspace{3em}

  \vspace*{-2\baselineskip}
  \begin{minipage}[t]{1.01\linewidth}
  \hdr{Propane/AT Concretization}{}
  \vspace*{-2\baselineskip}
  %
  \[ \begin{array}{lcl}
     \\
     \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
     \Con(l, \Gamma, f)              &=& \Sigma_i ~ f_i^{-1}(l) \\
     \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
     \Con(r_1 \cap r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cap \Con(r_2,\Gamma,f) \\
     \Con(!r, \Gamma, f)             &=& !\Con(r,\Gamma,f) \\
     \Con(r^*, \Gamma, f)            &=& \Con(r,\Gamma,f)^* \\%
     \Con(\Pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&
          \Pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\%
     \Con(\$x ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&%
         [~ \Pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~, \\%
         & & ~~~~~~~~~~~~~~~ \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (\Pfx,l) \in \Gamma(x) ~]  \\%
     \Con(p_1, \dots, p_n, \Gamma,f) &=& \Con(p_1, \Gamma,f), \dots, \Con(p_n, \Gamma,f) \\%

@@

  \vspace{2em}

  \begin{minipage}[t]{\linewidth}
  \hdr{mBGP Concretization}{}
  \vspace*{-2\baselineskip}
  %
  \[ \begin{array}{lcl}
     \\
     \Con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G)
        & = &
        \mathit{append}_i~ [~ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) ~]
        \\
     \Con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
        & = &
        \Con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, \Con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
        \\
     \Con(\Pfx \rightarrow {pc},\ell,\Gamma,f,G)
        & = &
        \Pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
        \\
     \Con(\$x \rightarrow {pc},\ell,\Gamma,f,G)
        & = &
        [~ \Pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (\Pfx, l) \in \Gamma(x) ~]
        \\
     \Con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G)
        & = &
        \Con(ma_1,o,\ell,\Gamma,f,G), \dots, \Con(ma_k,o,\ell,\Gamma,f,G)
        \\%
     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G)
        & = & \textbf{if}~ ns_1 = \{\text{start}\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)%

@@

  \caption{\sysname syntax and expansions.}
  \label{fig:syntax}
  %\vspace{-1em}
\end{figure*}%

\newpage

For reference, the full \sysname syntax as well as expansions from constraints into regular expressions are shown in Figure~\ref{fig:syntax}. The language includes constraints of the form $\CD{\Agg(pfx, \ensuremath{r_1 \rightarrow r_2})}$ that say that aggregation for summary prefix $\CD{pfx}$ will occur from any single location matching $\CD{\ensuremath{r_1}}$ to any location matching $\CD{\ensuremath{r_2}}$. For simplicity, we prove the substitution property for \sysname for the fragment without aggregation. mBGP syntax and compilation, as described in the paper, as well as concretization functions ($con$) are shown in Figure~\ref{fig:concretization}.

\subsection{Compilation}

We assume a particular router $l$ appears at most once in any mBGP specification.
We build configs using list-comprehension notation. For instance,
$[~ l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc) ~]$ denotes the mBGP policy
%
\[ \begin{array}{c}
  l_1 \rightarrow rc_{1},... \\
  ...           \\
  l_k \rightarrow rc_{k},... \\
\end{array} \]

@@

We also define concretization over the mBGP policy in a similar manner. We replace each abstract router configuration $l \rightarrow rc$ a new entry for each concrete location $\ell \in f^{-1}(l)$. The concrete location $\ell$ is passed as a parameter to $con$ to remember the current router.
%
To concretize a prefix policy with a template ($\$x \rightarrow pc$) we replace it with a sequence of policies, one for each prefix in context ($(pfx,l) \in \Gamma(x)$). Match action statements where the set of import neighbors is the singleton set containing the product graph start node $\{ start \}$ and we are not currently at looking at the router configuration for the location specified in the context $l$, then we drop the match action. This is denoted with the $\bullet$ symbol. Finally, to concretize a set of neighbors, we again use $f^{-1}$ to find the set of concrete neighbors under the inverse homomorphism, but then restrict it to those that are actually connected in the underlying concrete topology with $G.E$.

@@

The goal of this section is to prove that the concretization and compilation functions commute: 
$$con(compile(pol,G^A),\Gamma,f,G) = compile(con(pol,\Gamma,f), G)$$ 
That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values on after compilation is complete. Note that the theorem states that the resulting mBGP policies are actually syntactically equivalent and not semantically equivalent. First we need a few helper theorems about compilation.

@@

    \[ \begin{array}{ll}
        & compile(con(pol,\Gamma,f), G)  \\
                          & \\
                         =& compile_{mBGP}( \\
                          &  ~~~~ compile_{PG}(pfx_{11} ~\Path~ r'_{111} ~\Prefer~,\dots, ~\Prefer~ r'_{11k},G ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{1j} ~\Path~ r'_{1j1} ~\Prefer~,\dots, ~\Prefer~ r'_{1jk},G ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{i1} ~\Path~ r'_{i11} ~\Prefer~,\dots, ~\Prefer~ r'_{i1k},G ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{ij} ~\Path~ r'_{ij1} ~\Prefer~,\dots, ~\Prefer~ r'_{ijk},G ) \\
                          &  ) \\
    \end{array} \]

@@

    \[ \begin{array}{ll}
        & compile(pol,G^A)  \\
                      & \\
                     =& compile_{mBGP}( \\
                      & ~~~~ compile_{PG}(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k}, G^A ), \\
                      & ~~~~ \dots, \\
                      & ~~~~ compile_{PG}(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r'_{ik}, G^A ), \\
                      & ) \\
    \end{array} \]

@@

  \[ \begin{array}{l}
     con(\textbf{compile}_\textbf{mBGP}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) ), \Gamma,f,G) \\
  \end{array} \]%

Unfold definition of $\text{compile}_\text{mBGP}$

@@

  \[ \begin{array}{l}
     = \textbf{compile}_\textbf{mBGP}( (pfx_{11},PG_{11},ord_{11}), \dots, (pfx_{ij},PG_{ij},ord_{ij}) ) \\
  \end{array} \]%
